Visually pleasing knot projections

### 2023-01-31 inst/jma_rebuttal_2023_01_30.tex

RE: Link projections: In a future system, the planning for handling
links should come in right at the beginning.  It is not at all clear
why "Each component would have its own badness."

Many of the important badness functions (e.g. separations of nodes or
of non-crossing curve segments) are based purely on local geometry and
need not know what component of a link they refer to.  Perhaps the
overall length of a knot or of a link-component is not a good metric,
and should be replaced with some other functions of the length of
curve segments between crossings.

Some detailed comments on manuscript R2:

Page 6, line 20: How many (x,y) pairs are there?
\textcolor{blue}{\\Object {\tt k76} has a total of 49 lines and I have
  indicated this in the text.  Old text: ``Above we see only the first
  six lines of the object".  New text: ``The object has 49 lines, of
  which only the first six are shown".\\ \\}

Page 6, Line 36: Why ``$\mathbb{R}^{50}$"? - Are there a total of 50
parameters?  What are they?  \textcolor{blue}{\\This was not clear and
  I have rephased.  Old text: ``The optimization typically proceeds
  over $\mathbb{R}^{50}$\ldots". New text: ``The optimization
  proceeds over $\mathbb{R}^n$ where $n$ is the number of parameters
  needed to specify the path; typically $n\simeq 50$ for the knots
  presented here".\\ \\}

### 2023-01-31 inst/jma_rebuttal_2023_01_30.tex

Page 6, line 20: How many (x,y) pairs are there?
\textcolor{blue}{\\Object {\tt k76} has a total of 49 lines and I have
  indicated this in the text.  Old text: ``Above we see only the first
  six lines of the object".  New text: ``The object has 49 lines, of
  which only the first six are shown".\\ \\}

Page 6, Line 36: Why ``$\mathbb{R}^{50}$"? - Are there a total of 50
parameters?  What are they?  \textcolor{blue}{\\This was not clear and
  I have rephased.  Old text: ``The optimization typically proceeds
  over $\mathbb{R}^{50}$\ldots". New text: ``The optimization
  proceeds over $\mathbb{R}^n$ where $n$ is the number of parameters
  needed to specify the path; typically $n\simeq 50$ for the knots
  presented here".\\ \\}

Page 6, Line 39: ``... the overall bending energy." {\tt ->>} 'minimizing
overall bending energy.'
\textcolor{blue}{\\Fixed\\ \\}

Page 6, Line 42:  What is "{\tt > b <}" ?
\\ \\
\textcolor{blue}{This is just a detail of standard R syntax.  The
  first ``{\tt > }" is just the R prompt; letter {\tt b} is just a
  variable; and the symbol ``{\tt <-}" usually has a gloss of
  ``becomes".  Thus {\tt b <- 4} is read ``{\tt b} becomes 4". The
  reason I need a variable is that I want to show the result of
  applying two functions, {\tt total\_crossing\_angles()} and {\tt
    total\_bending\_energy()}, to the same variable {\tt b}.}

@@

Figures 3 and 5: Try running these figures with only 50 points (and
circles) for each Bezier segment.

Figure 4 caption: Much of the explanation of "7 3" versus "3 7" is
already in the main text.

Page 8, Line 60: "Why 64 real variables"?  What are they?  How does
this agree with "R50" on page 6 ?

Figure 7: Where does the spiky artifact in the upper right lobe come
from?  \textcolor{blue}{\\I see nothing in figure 7 that could be so
  described.  I expect this is a rendering issue, if so it will be
  sorted out at proofreading stage.\\ \\}

### 2023-01-31 inst/jma_knot.tex
fixes #88
fixes #96

Object~{\tt k76} is stored as an object of class {\tt inkscape}: a
two-column matrix with rows corresponding to the node and handle
positions of the inkscape path.  Above we see only the first six lines
of the object.  Inkscape representation has a certain amount of
redundancy as knot paths have handles which are symmetrically placed
with respect to nodes; also, the first node is the same as the last
for the loop is closed.  The package can coerce inkscape objects to
other forms, specifically {\tt minobj} objects, which contain no
redundancy (the position of each node, as well as one of the handles,
is stored); or {\tt controlpoints} objects, which allow for easy
construction of Bezier interpolation between nodes.

@@

Thus, using the same notation as before, nodes~11 and~13 are
symmetrical about the vertical axis, nodes~2 and~12 are on the
vertical axis.  The {\tt Mrot} argument specifies sets of nodes that
map to themselves under rotation.  The top line of {\tt Mrot}
indicates that nodes 12, 4, 16, 8, and~20 are concyclic.  An example
of a rotationally symmetric knot is given in Figure~\ref{orn20}.

>>>>

Object~{\tt k76} is stored as an object of class {\tt inkscape}: a
two-column matrix with rows corresponding to the node and handle
positions of the inkscape path.   The object has 49 lines, of which only the  first six are shown.  Inkscape representation has a certain amount of
redundancy as knot paths have handles which are symmetrically placed
with respect to nodes; also, the first node is the same as the last
for the loop is closed.  The package can coerce inkscape objects to
other forms, specifically {\tt minobj} objects, which contain no
redundancy (the position of each node, as well as one of the handles,
is stored); or {\tt controlpoints} objects, which allow for easy
construction of Bezier interpolation between nodes.

@@

Thus, using the same notation as before, nodes~11 and~13 are
symmetrical about the vertical axis, nodes~2 and~12 are on the
vertical axis.  The {\tt Mrot} argument specifies sets of nodes that
map to themselves under rotation.  The top line of {\tt Mrot}
indicates that nodes 12, 4, 16, 8, and~20 are concyclic.  An example
of a knot with pure rotational symmetry, rather than dihedral
symmetry, is given in Figure~\ref{orn20}.
